---
editor_options: 
  markdown: 
    wrap: 72
  chunk_output_type: inline

output: pdf_document
geometry: "left=1in,right=3in,top=1in,bottom=1in"
---

rm(list = ls()) #nettoie l'environnement

# Loading and shaping data --------------------------------------------------

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(ggplot2)
library(ggsignif)
library(ggpubr)
library(Publish)
library(dplyr) #pour la SQL
theme_set(theme_classic())
library(latex2exp)
library(reshape2) # pour passer de wide data à long data


file <- "04_26_prepF_pourR.csv"
res <- read.csv(file, sep = ";", header = TRUE)

file3 <- "lamelles_surL_F.csv"
lamelles_sur_Sc <- read.csv(file3, sep = ";", header = TRUE)

file4 <- "lamelles_F.csv"
lamelles <- read.csv(file4, sep = ";", header = TRUE)

file5 <- "mitocS_F.csv"
mitocS <- read.csv(file5, sep = ";", header = TRUE)

file6 <- "mito_surS_F.csv"
mitoc_surS <- read.csv(file6, sep = ";", header = TRUE)

scale =  0.2983 #pixels per nm
scale3 = 0.5967
```

Scaling values and shaping dataframe
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
#/!\ NE PAS RÉEXECUTER!!!!!
res$surface_cell[res$Sectioning != 3] <- res$surface_cell[res$Sectioning != 3]/(scale*scale)
res$surface_cell[res$Sectioning == 3] <- res$surface_cell[res$Sectioning == 3]/(scale3*scale3)
res$S_vacuole_tot[res$Sectioning != 3] <- res$S_vacuole_tot[res$Sectioning != 3]/(scale*scale)
res$S_vacuole_tot[res$Sectioning == 3] <- res$S_vacuole_tot[res$Sectioning == 3]/(scale3*scale3)
res$S_lipid_tot[res$Sectioning != 3] <- res$S_lipid_tot[res$Sectioning != 3]/(scale*scale)
res$S_lipid_tot[res$Sectioning == 3] <- res$S_lipid_tot[res$Sectioning == 3]/(scale3*scale3)
res$S_sucre_tot[res$Sectioning != 3] <- res$S_sucre_tot[res$Sectioning != 3]/(scale*scale)
res$S_sucre_tot[res$Sectioning == 3] <- res$S_sucre_tot[res$Sectioning == 3]/(scale3*scale3)
res$S_noyau_zoom[res$Sectioning != 3] <- res$S_noyau_zoom[res$Sectioning != 3]/(scale*scale)
res$S_noyau_zoom[res$Sectioning == 3] <- res$S_noyau_zoom[res$Sectioning == 3]/(scale3*scale3)
res$S_euchromatine[res$Sectioning != 3] <- res$S_euchromatine[res$Sectioning != 3]/(scale*scale)
res$S_euchromatine[res$Sectioning == 3] <- res$S_euchromatine[res$Sectioning == 3]/(scale3*scale3)
res$S_nucleole_zoom[res$Sectioning != 3] <- res$S_nucleole_zoom[res$Sectioning != 3]/(scale*scale)
res$S_nucleole_zoom[res$Sectioning == 3] <- res$S_nucleole_zoom[res$Sectioning == 3]/(scale3*scale3)
res$S_heterochromatin[res$Sectioning != 3] <- res$S_heterochromatin[res$Sectioning != 3]/(scale*scale)
res$S_heterochromatin[res$Sectioning == 3] <- res$S_heterochromatin[res$Sectioning == 3]/(scale3*scale3)

res$division[res$division == "1*"] <- 1

lamelles[c(65:99,164:198,264:297),2] <- lamelles[c(65:99,164:198,264:297),2]/(scale3)
lamelles[c(1:64,100:163,199:263,298:555),2] <- lamelles[c(1:64,100:163,199:263,298:555),2]/(scale)

mitocS$value[mitocS$Lumiere == "Dark3"] <- mitocS$value[mitocS$Lumiere == "Dark3"]/(scale3*scale3)
mitocS$value[mitocS$Lumiere != "Dark3"] <- mitocS$value[mitocS$Lumiere != "Dark3"]/(scale*scale)
mitocS$Lumiere[mitocS$Lumiere == "Dark3"] <- "Dark"

res$pourcent_noyau <- res$S_noyau_zoom/res$surface_cell
res$pourcent_nucleole <- res$S_nucleole_zoom/res$surface_cell
res$fusion_ou_pas <- res$X.fusion.si.chloro.visible.et.flou...2
res$fusion_ou_pas[res$fusion_ou_pas > 1] <- 1

res <- melt(res, a.rm = FALSE, id.vars = c("Lumiere", "Nom","division"))
res$value <- as.double(res$value) #they were converted into strings
```
Caution : no Sec3 taken into account for mitochondriae

# Functions used later on 

## Statistical analysis
```{r, warning = FALSE, message = FALSE, results = 'asis'}
function_stat <- function(df) {
  df_d <- filter(df, Lumiere == 'Dark')$value
  df_l <- filter(df, Lumiere == 'Light')$value
  n_d <- length(df_d) #number of points measured for the dark
  n_l <- length(df_l)
  large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise
  shapirotxt <- ""
  vartxt <- ""

  if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    cat("Population size is too small to compare and/or all measures are the same \n.")
    p_value = 1
    return(p_value)
  }
  
  else {
    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer((normal_d > 0.05) & (normal_l > 0.05))
    if (N == 1) { #samples normally distributed
      shapirotxt <- paste0("Samples are normally distributed (shapiro test) \n *p-value dark = ", round(normal_d,3), ", p-value light = ", round(normal_l,3),".*\n")
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances, F test
        vartxt <- paste0("Variances are considered equal, *p-value = ", round(var.test(df_d,df_l)$p.value,3),".*\n")
        p_value <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%,"
      }
      else { #different variances
        vartxt <- paste0("Variances are not equal, *p-value = ", round(var.test(df_d,df_l)$p.value,3),".*\n")
        p_value <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%,"
      }
    }
    
    else{ #variables not normally distributed 
       shapirotxt <- paste0("Samples are not normally distributed (shapiro test),\n *p-value dark = ", round(normal_d,3), ", p-value light = ", round(normal_l,3),".*\n")
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        p_value <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%,"
      }
      if (large_sample == 0) {
        p_value <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%,"
      }
    }
    cat(test_used, "**p-value = ", round(p_value,5),"**","\n")
    return(p_value)
  }
}
```

```{r, warning = FALSE, message = FALSE, results = 'asis'}
comp_freq <- function(df) {
  dat <- data.frame(row.names = c("Dark","Light"), No = c(df[1,3]$count,df[3,3]$count), Yes = c(df[2,3]$count,df[4,3]$count))
  
  n1 <- dat[1,1] + dat[1,2]
  n2 <- dat[2,1] + dat[2,2]
  
  if ( (n1 < 3) == T | (n2 < 3) == T | is.na(n1) == T |
      is.na(n2) == T ) {
    return("Chi2 can't be applied")
  }
  
  f <- (dat[1,2] + dat[2,2])/(n1+n2)
  
  if ( (n1*f <5) == T | (n2*f<5) == T| (n1*(1-f)<5) == T | 
       (n2*(1-f)<5) ==T | ((n1+n2) < 50) == T ) {
    return("Chi2 can't be applied")
  }
  
  pvalue <- chisq.test(dat)$p.value
  
  psign <- c("NS","*", "**", "***")
  pindex <- as.integer(pvalue >= 0.05) + 
    as.integer((pvalue < 0.05) & (pvalue >= 0.01))*2 + 
    as.integer((pvalue < 0.01) & (pvalue >= 0.001))*3 +
    as.integer(pvalue < 0.001)*4
  
  L <- data.frame(c(psign[pindex],pvalue))
  knitr::kable(L, caption = "Red = Present, Blue = Absent", align = "cccc",
               col.names = c("p-value"))
}
```

## Plot

We have 3 types of plots : scaled plots, pourcent plots and proportion plots

### Scaled plot
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, dpi =300, fig.align = "center"}
scaled_plot <- function(df,pvalue, title, saving_name) { 
  psign <- c("NS","*", "**", "***")
  pindex <- as.integer(pvalue >= 0.05) + 
    as.integer((pvalue < 0.05) & (pvalue >= 0.01))*2 + 
    as.integer((pvalue < 0.01) & (pvalue >= 0.001))*3 +
    as.integer(pvalue < 0.001)*4
  cat("\n")
  cat("## ", title)
  
  plot1 <- ggplot(df, aes(x=Lumiere , y=value/1000000, fill= Lumiere)) + 
    geom_violin() + 
    geom_jitter(size = 0.2, width = 0.1, height = 0.05) +
    scale_fill_manual(labels = c(paste("Dark (N=",length(filter(df, Lumiere == "Dark")[,2]),")", sep = ""),
                                 paste("Light (N=",length(filter(df, Lumiere == "Light")[,2]), ")", sep = "")),
                      values = c("#f2f2f2", "#feefae")) +
    stat_summary(fun = "mean", geom = "crossbar", color = "#C34343", 
                size = 0.3) + 
    stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", 
                 color = "#C34343",
                 width = 0.4, alpha = 0.7) + 
    ylab(TeX(r'(µm$^{2}$)')) + 
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.title.y = element_text(size = 15),
          axis.text.y = element_text(size = 15), 
          legend.title = element_blank(), 
          legend.text = element_text(size = 15, margin = margin(0,2,0,0, unit = "in"))) +
    geom_signif(annotations = c(psign[pindex]), y_position = c(1.1*max(df$value)/1000000), xmin = c(1), xmax = c(2))
  
   ggsave(plot1, file=paste0(saving_name,".png"), width = 5, height = 5.8, units = "in", dpi=300)
   
  cat("\n\n\n")
  function_stat(df)
  cat("\n\n\n")
  print(plot1)
  cat("\n\n\n")
  }
  
```
 
### Pourcentage plot

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, dpi = 300,  fig.align = "center"}

pourcent_plot <- function(df, pourcent, pvalue, title, saving_name) { 
  #pourcent => do we multiply value by 1 or by 100?
  
  psign <- c("NS","*", "**", "***")
  pindex <- as.integer(pvalue >= 0.05) + 
    as.integer((pvalue < 0.05) & (pvalue >= 0.01))*2 + 
    as.integer((pvalue < 0.01) & (pvalue >= 0.001))*3 +
    as.integer(pvalue < 0.001)*4
  cat("\n")
  cat("## ", title)

  plot2 <- ggplot(df, aes(x=Lumiere , y=value*pourcent, fill= Lumiere)) + 
    geom_violin() + 
    geom_jitter(size = 0.2, width = 0.1, height = 0.05) +
    scale_fill_manual(labels = c(paste("Dark (N=",length(filter(df, Lumiere == "Dark")[,2]),")", sep = ""),
                                 paste("Light (N=",length(filter(df, Lumiere == "Light")[,2]), ")", sep = "")),
                      values = c("#f2f2f2", "#feefae")) +
    stat_summary(fun = "mean", geom = "crossbar", color = "#C34343", 
                size = 0.3) + 
    stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", 
                 color = "#C34343",
                 width = 0.4, alpha = 0.7) + 
    ylab("%") + 
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.title.y = element_text(size = 15),
          axis.text.y = element_text(size = 15), 
          legend.title = element_blank(), 
          legend.text = element_text(size = 15, margin = margin(0,2,0,0, unit = "in")))+
    geom_signif(annotations = c(psign[pindex]), y_position = c(1.1*max(df$value)*pourcent), xmin = c(1), xmax = c(2))

  ggsave(plot2, file=paste0(saving_name,".png"), width = 5, height = 5.8, units = "in", dpi=300)
   
  cat("\n\n\n")
  function_stat(df)
  cat("\n\n\n")
  print(plot2)
  cat("\n\n\n")
  }
  
```
 
 
### Unscaled plot

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, dpi = 300, fig.align = "center"}

unscaled_plot <- function(df, pvalue, title, saving_name, factor = 1) { 
  #pourcent => do we multiply value by 1 or by 100?
  
  psign <- c("NS","*", "**", "***")
  pindex <- as.integer(pvalue >= 0.05) + 
    as.integer((pvalue < 0.05) & (pvalue >= 0.01))*2 + 
    as.integer((pvalue < 0.01) & (pvalue >= 0.001))*3 +
    as.integer(pvalue < 0.001)*4
  cat("\n")
  cat("## ", title)

  plot2 <- ggplot(df, aes(x=Lumiere , y=value*factor, fill= Lumiere)) + 
    geom_violin() + 
    geom_jitter(size = 0.2, width = 0.1, height = 0.05) +
    scale_fill_manual(labels = c(paste("Dark (N=",length(filter(df, Lumiere == "Dark")[,2]),")", sep = ""),
                                 paste("Light (N=",length(filter(df, Lumiere == "Light")[,2]), ")", sep = "")),
                      values = c("#f2f2f2", "#feefae")) +
    stat_summary(fun = "mean", geom = "crossbar", color = "#C34343", 
                size = 0.3) + 
    stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", 
                 color = "#C34343",
                 width = 0.4, alpha = 0.7) + 
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.title.y = element_blank(),
          axis.text.y = element_text(size = 15), 
          legend.title = element_blank(), 
          legend.text = element_text(size = 15, margin = margin(0,2,0,0, unit = "in"))) + 
    geom_signif(annotations = c(psign[pindex]), y_position = c(1.1*max(df$value)*factor), xmin = c(1), xmax = c(2)) 

   ggsave(plot2, file=paste0(saving_name,".png"), width = 5, height = 5.8, units = "in", dpi=300)
   
  cat("\n\n\n")
  function_stat(df)
  cat("\n\n\n")
  print(plot2)
  cat("\n\n\n")
  }
  
```

### Diagram plot
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, dpi = 300, fig.align = "center"}

#Only takes values that are 1 or 0
diagram_plot <- function(df, title, saving_name) { 
  if(length(unique(df$value)) > 2){
    return("Verify data format")
  }
  cat("\n")
  cat("## ", title)
  
rm(res2)
res2 <- df %>% 
  group_by(Lumiere, value) %>% 
  summarise(count = n()) %>% 
  mutate(perc = count/sum(count))

dprop <- ggplot(filter(res2, Lumiere == "Dark"), 
               aes(x = "", y = perc*100, fill=factor(value))) +
geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%",sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

lprop <- ggplot(filter(res2, Lumiere == "Light"), 
               aes(x = "", y = perc*100, fill=factor(value))) +
  geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%",sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

fig <- ggarrange(dprop, lprop, ncol = 2, nrow = 1,labels = c("Dark", "Light"), label.y = 0.3, label.x = 0.25)
cat("\n\n")
print(fig)

ggsave(fig, file=paste0(saving_name,".png"), width = 5, height = 5.8, units = "in", dpi=300)

comp_freq(res2)
  }
```

# Main code

## Cell area
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- filter(res, division == 0)
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3, function_stat(res3), "Non-dividing cells area", "Scell_nondiv")
function_stat(res3)


res3 <- res
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3, function_stat(res3), "All cells area", "Scell_all")


res3 <- res
res3 <- res3 %>% filter(variable == "surface_cell")  %>% filter(value/1000000 > 0.5)
scaled_plot(res3, function_stat(res3), "All cells area - one outlier removed", "Scell_all_without1")



res3 <- filter(res, division != 0)
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3,function_stat(res3),"Dividing cells area", "Scell_div")

```

## Proportion de cellules en division

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res$div_ou_pas <- res$division
res$div_ou_pas[res$div_ou_pas >0] <- 1

rm(res2)
res2 <- res %>% 
  group_by(Lumiere, div_ou_pas) %>% 
  summarise(count = n()) %>% 
  mutate(perc = count/sum(count))

dprop <- ggplot(filter(res2, Lumiere == "Dark"), 
               aes(x = "", y = perc*100, fill=factor(div_ou_pas))) +
 geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%", sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

lprop <- ggplot(filter(res2, Lumiere == "Light"), 
               aes(x = "", y = perc*100, fill=factor(div_ou_pas))) +
  geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%",sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

fig <- ggarrange(dprop, lprop, ncol = 2, nrow = 1,labels = c("Dark", "Light"), label.y = 0.3, label.x = 0.25)
fig
comp_freq(res2)
```

## Nombre de golgis

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- res %>% filter(variable == "golgi") %>% filter(is.na(value)==F)
unscaled_plot(res3, function_stat(res3), "Number of golgi", "golgi")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "golgi") %>% filter(is.na(value) == F)
res3$value[res3$value >0] <- 1
diagram_plot(res3,"Proportion of images with a golgi","golgioupa")
```

## Surface Vacuole

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "X.S_V.S_cell") %>% filter(value != 0)
pourcent_plot(res3,1, function_stat(res3), "Vacuole's proportion of the cells - if > 0%", "vacPourcent_sivac")

res3 <- res %>% filter(variable == "X.S_V.S_cell")
pourcent_plot(res3,1, function_stat(res3), "Vacuole's proportion of the cell", "vacPourcent_all")

res3 <- res %>% filter(variable == "S_vacuole_tot") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Vacuole's area in the cell - if non null", "vacS_sivac")
 ##
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "nb_vacuoles")
res3$value[res3$value >0] <- 1
diagram_plot(res3,"Proportion of images with a vacuole","vacoupa")
```

## Surface lipides

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "X.S_L.S_cell") %>% filter(value != 0)
pourcent_plot(res3, 1, function_stat(res3), "Lipid content of the cells - if > 0%", "lipidPourcent_silip")

res3 <- res %>% filter(variable == "X.S_L.S_cell") %>% filter(value != 0) %>% filter(value < 100)
pourcent_plot(res3,1, function_stat(res3), "Lipid content of the cells - if > 0% and <100%", "lipidPourcent_silip_sansout")

res3 <- res %>% filter(variable == "S_lipid_tot") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Lipid content of the cells - if > 0µm2", "lipidS_silip")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "nb_lipids")
res3$value[res3$value >0] <- 1
diagram_plot(res3,"Proportion of images with lipid·s","lipoupa")
```

## Surface sucres

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "X.S_s.S_cell")%>% filter(value != 0)

pourcent_plot(res3,1, function_stat(res3), "Chrysolaminarin's proportion of the cell - if > 0%", "chrysoPourcent_siChryso")

res3 <- res %>% filter(variable == "X.S_s.S_cell") %>% filter(value != 0) %>% filter(value < 20)
pourcent_plot(res3,1, function_stat(res3), "Chrysolaminarin's proportion of the cell - if > 0%, one outlier removed", "chrysoPourcent_siChryso_sansout")

res3 <- res %>% filter(variable == "S_sucre_tot") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Chrysolaminarin's area in the cell - if non null", "chrysoS_sichryso")


res3 <- res %>% filter(variable == "S_sucre_tot") %>% filter(value != 0) %>% filter(value/1000000 < 0.5)
scaled_plot(res3, function_stat(res3), "Chrysolaminarin's area in the cell - if non null, one outlier removed", "chrysoS_sichryso_sansout")

res3 <- res %>% filter(variable == "nb_sucres")
unscaled_plot(res3, function_stat(res3),title = "Number of chrysolaminarin droplets", "nbsucres")

res3 <- res %>% filter(variable == "nb_sucres") %>% filter(value>0)
unscaled_plot(res3, function_stat(res3),title = "Number of chrysolaminarin droplets, if > 0", "nbsucres_sans0")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis',fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "nb_sucres")
res3$value[res3$value >0] <- 1
diagram_plot(res3,"Proportion of images with chrysolaminarin","sucroupa")
```

## Largeur lamelle

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- lamelles %>% filter(value != 0)
unscaled_plot(res3, function_stat(res3), "Lamellae width (nm) - if > 0nm", "lamellesL")

res3 <- lamelles_sur_Sc %>% filter(10*value > 0)
unscaled_plot(res3, function_stat(res3), "Lamellae width normalized by the cell's dimension", "lamelle_surS", factor = 10)

res3 <- lamelles_sur_Sc %>% filter(10*value > 0) %>% filter(value < 1)
unscaled_plot(res3, function_stat(res3), "1000*Lamellae width normalized by the cell's dimension - 3 outliers removed", "lamelle_surS_no_out", factor = 10)

```

## Heterochromatine sur euchromatine

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "hetero.euch") %>% filter(is.na(value) == F)
res3$value <- res3$value/100
unscaled_plot(res3, function_stat(res3),"DNA condensation ratio (heterochromatin/euchromatin)", "heteroeuch_all")


res3 <- res %>% filter(variable == "hetero.euch") %>% 
  filter(is.na(value) == F) %>%
  filter(value > 0)
res3$value <- res3$value/100
unscaled_plot(res3, function_stat(res3),"DNA condensation ratio (heterochromatin/euchromatin) - 1 outlier removed", "heteroeuch_all_sans_out")


res3 <- res %>% filter(division == 0) %>%  
  filter(variable == "hetero.euch") %>% 
  filter(is.na(value) == F) %>%
  filter(value >0)
res3$value <- res3$value/100
unscaled_plot(res3, function_stat(res3),"DNA condensation ratio (heterochromatin/euchromatin) - non dividing cells, one outlier removed", "heteroeuch_all_div0")

```

## Comparison of DNA condensation levels between dividing, recently divided and non dividing cells
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
df <- res %>% filter(variable == "hetero.euch") %>% filter(value > -100)


pvalues <- c(0,0,0)
pindex <- c(0,0,0)


##

df_d <- filter(df, division == 0)$value
df_l <- filter(df, division == 1)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[1] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){
    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[1] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[1],5)))
}

##

df_d <- filter(df, division == 1)$value
df_l <- filter(df, division == 2)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

  if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[2] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[2] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[2],5)))
  }

##

df_d <- filter(df, division == 0)$value
df_l <- filter(df, division == 2)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

  if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[3] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[3] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[3],5)))
  }
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, fig.align = "center"}

for (i in c(1,2,3)) {
  psign <- c("NS","*", "**", "***")
  pindex[i] <- as.integer(pvalues[i] >= 0.05) + 
      as.integer((pvalues[i] < 0.05) & (pvalues[i] >= 0.01))*2 + 
      as.integer((pvalues[i] < 0.01) & (pvalues[i] >= 0.001))*3 +
      as.integer(pvalues[i] < 0.001)*4
}
  
df[33,3] = 1
  
plot2 <- ggplot(df, aes(x=factor(division) , y=value, fill = factor(division))) + 
    geom_violin() + 
    geom_jitter(size = 0.2, width = 0.1, height = 0.05) +
    stat_summary(fun = "mean", geom = "crossbar", color = "black", 
                size = 0.3) + 
    stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", 
                 color = "black",
                 width = 0.4, alpha = 0.7) + 
    theme(axis.title.x=element_blank(),
          axis.title.y = element_text(size = 15),
          axis.text.y = element_text(size = 15), 
          legend.position = "none",
          plot.title = element_text(size = 15, margin = margin(c(0,0,0.5,0), unit = "in")))+
  scale_fill_manual(values = c("#F7C090", "#feefae", "#A9DFD0")) +
  scale_x_discrete(labels = c("Non-dividing cell", "Recently divided cell", "Dividing cell")) +
    geom_signif(annotations = c(psign[pindex]), y_position = c(270,270,310), xmin = c(1.02,2.02,1.02), xmax = c(1.98,2.98,2.98)) +
    ggtitle("DNA condensation, depending on the state of the cell")
 
  print(plot2)
  ggsave(plot2, file=paste0("DNA condensation",".png"), width = 5, height = 5.8, units = "in", dpi=300)

```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "S_noyau_zoom")
res3$value[res3$value != 0] <- 1
diagram_plot(res3,"Proportion of images with visible nucleus","noyauoupa")
```

## Surface noyau

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- res %>% filter(variable == "S_noyau_zoom") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Nucleus area", "nucleusS")

res3 <- res %>% filter(variable == "pourcent_noyau") %>% filter(value != 0) %>%
  filter(value < 1)
pourcent_plot(res3, 100, function_stat(res3), "Nucleus area proportion", "nucleuspourcent")
```

## Surface nucleole

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "S_nucleole_zoom") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Nucleolus area", "nucleolusS")

res3 <- res %>% filter(variable == "pourcent_nucleole") %>% filter(value != 0) %>%
  filter(value < 1)
pourcent_plot(res3, 100, function_stat(res3), "Nucleolus area proportion", "nucleoluspourcent")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- res %>% filter(variable == "S_nucleole_zoom") %>% filter(value != 0)
scaled_plot(res3, function_stat(res3), "Nucleolus area", "nucleolusS")

res3 <- res %>% filter(variable == "pourcent_nucleole") %>% filter(value != 0) %>%
  filter(value < 1)
pourcent_plot(res3, 100, function_stat(res3), "Nucleolus area proportion", "nucleoluspourcent")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
dnoyau <- sum(res[res$Lumiere == "Dark" & res$variable =="S_noyau_zoom",]$value > 0)
lnoyau <- sum(res[res$Lumiere == "Light" & res$variable =="S_noyau_zoom",]$value > 0)
dnucleole <- sum(res[res$Lumiere == "Dark" & res$variable =="S_nucleole_zoom",]$value > 0)
lnucleole <- sum(res[res$Lumiere == "Light" & res$variable =="S_nucleole_zoom",]$value > 0)

res2 <- data.frame(Lumiere = c("Dark","Dark","Light","Light"),
                   value = c(0,1,0,1), 
                   count = c(dnoyau-dnucleole, dnucleole,lnoyau-lnucleole,lnucleole),
                   perc = c((dnoyau-dnucleole)/dnoyau, dnucleole/dnoyau, (lnoyau-lnucleole)/lnoyau, lnucleole/lnoyau))

saving_name = "nucleoloupa"

dprop <- ggplot(filter(res2, Lumiere == "Dark"), 
               aes(x = "", y = perc*100, fill=factor(value))) +
geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%",sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

lprop <- ggplot(filter(res2, Lumiere == "Light"), 
               aes(x = "", y = perc*100, fill=factor(value))) +
  geom_bar(stat="identity",color = "white") +
  geom_label(aes(x=1.4, label = paste(round(perc*100),"%",sep = "")),
            position = position_stack(vjust = 0.5, reverse = FALSE),
            size = 7, alpha = 0.3) +
  coord_polar(theta = "y") +
  theme_void() + 
  scale_fill_manual(values = c("#A7B9FD","#FAAFAF", "white")) +
  theme(legend.position = "none")

fig <- ggarrange(dprop, lprop, ncol = 2, nrow = 1,labels = c("Dark", "Light"), label.y = 0.3, label.x = 0.25)
fig

ggsave(fig, file=paste0(saving_name,".png"), width = 5, height = 5.8, units = "in", dpi=300)

df <- res2
##Comp freq
#The scripted function can't be used because values in df are not in the same format
comp_nucleolus <- function(df) {
  dat <- data.frame(row.names = c("Dark","Light"), No = c(df[1,3],df[3,3]), Yes = c(df[2,3],df[4,3]))
  n1 <- dat[1,1] + dat[1,2]
  n2 <- dat[2,1] + dat[2,2]
  if ( (n1 < 3) == T | (n2 < 3) == T | is.na(n1) == T | is.na(n2) == T ) {
      return("Chi2 can't be applied")
    }
    
  f <- (dat[1,2] + dat[2,2])/(n1+n2)
  
  if ( (n1*f <5) == T | (n2*f<5) == T| (n1*(1-f)<5) == T | 
         (n2*(1-f)<5) ==T | ((n1+n2) < 50) == T ) {
    return("Chi2 can't be applied")
  }
  
  pvalue <- chisq.test(dat)$p.value
  
  psign <- c("NS","*", "**", "***")
  pindex <- as.integer(pvalue >= 0.05) + 
    as.integer((pvalue < 0.05) & (pvalue >= 0.01))*2 + 
    as.integer((pvalue < 0.01) & (pvalue >= 0.001))*3 +
    as.integer(pvalue < 0.001)*4
  
  L <- data.frame(c(psign[pindex],pvalue))
  knitr::kable(L, caption = "Red = Present, Blue = Absent", align = "cccc",
               col.names = c("p-value"))
}
comp_nucleolus(df)
rm(saving_name, lnoyau, dnoyau, lnucleole, dnucleole)
```

## Globules chloroplastes

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- res %>% filter(variable == "X.globules.chloro") %>% filter(value != 0)
unscaled_plot(res3, function_stat(res3), "Plastoglobuli number", "globules")
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "X.globules.chloro")
res3$value[res3$value >0] <- 1
res3$value[is.na(res3$value) == T] <- 0
diagram_plot(res3,"Proportion of images with plastoglobuli","globoupa")
```

## Flou chloroplaste

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}

res3 <- res %>% filter(variable == "X.flou.si.chloro.visible")
res3$value[res3$value < 2] <- 0
diagram_plot(res3,"Proportion of images with plastoglobuli","globoupa")
```

## Fusion lamelles

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width=4, fig.align = "center"}
res3 <- res %>% filter(variable == "fusion_ou_pas") %>% filter(is.na(value) == F)
diagram_plot(res3,title = "Lamellae fusion","fusionoupa")
```

## Crêtes mitochondriales

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
res3 <- mitocS %>% filter(is.na(value) == F)
unscaled_plot(res3, function_stat(res3), "Mitochondrial cristae area (nm2)", "mitoS")

res3 <- mitoc_surS %>% filter(is.na(value) == F) %>% filter(value < 100)
res3$value <- res3$value*100000
unscaled_plot(res3, function_stat(res3), "Mitochondrial cristae area proportion (compared to cell area)", "mitopourcent")

res3 <- mitoc_surS %>% filter(is.na(value) == F) %>% filter(value<1)
res3$value <- res3$value*100000
unscaled_plot(res3, function_stat(res3), "Mitochondrial cristae area proportion (compared to cell area*10,000) - outliers removed", "mitopourcent_nooutliers")
```


# Aditional plots

### Dividing versus non-dividing cell area (light only)

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}

res3 <- filter(res, Lumiere == "Light") %>% filter(division <2)
res3$Lumiere[res3$division > 0] <- "Dark" #recently divided cells will be annotated as dark cells
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3, function_stat(res3), "Recently divided cells vs still cells", "Light_recentlyvsnondiv")

res3 <- filter(res, Lumiere == "Light") %>% filter(division != 1)
res3$Lumiere[res3$division > 0] <- "Dark" #recently divided cells will be annotated as dark cells
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3, function_stat(res3), "Dividing vs still cells area", "Light_divvsnondiv")

res3 <- filter(res, Lumiere == "Dark") %>% filter(division <2)
res3$Lumiere[res3$division == 0] <- "Light" #recently divided cells will be annotated as dark cells
res3 <- res3 %>% filter(variable == "surface_cell")
scaled_plot(res3, function_stat(res3), "Recently divided cells vs still cells", "Dark_recentlyvsnondiv")

```

### Storage content

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
file <- "04_26_prepF_pourR.csv"
res4 <- read.csv(file, sep = ";", header = TRUE)

res4$surface_cell[res4$Sectioning != 3] <- res4$surface_cell[res4$Sectioning != 3]/(scale*scale)
res4$surface_cell[res4$Sectioning == 3] <- res4$surface_cell[res4$Sectioning == 3]/(scale3*scale3)
res4$S_vacuole_tot[res4$Sectioning != 3] <- res4$S_vacuole_tot[res4$Sectioning != 3]/(scale*scale)
res4$S_vacuole_tot[res4$Sectioning == 3] <- res4$S_vacuole_tot[res4$Sectioning == 3]/(scale3*scale3)
res4$S_lipid_tot[res4$Sectioning != 3] <- res4$S_lipid_tot[res4$Sectioning != 3]/(scale*scale)
res4$S_lipid_tot[res4$Sectioning == 3] <- res4$S_lipid_tot[res4$Sectioning == 3]/(scale3*scale3)

res4$storage <- res4$S_lipid_tot + res4$S_vacuole_tot
res4$storage_surS <- res4$storage/res4$surface_cell
res4 <- melt(res4, a.rm = FALSE, id.vars = c("Lumiere", "Nom","division"))
res4$value <- as.double(res4$value)

res3 <- res4 %>% filter(variable == "storage")
scaled_plot(res3, function_stat(res3), "Lipid + chrysolaminarin area", "lipidchryso")

res3 <- res4 %>% filter(variable == "storage_surS")
pourcent_plot(res3,100, function_stat(res3), "Lipid + chrysolaminarin proportion of the cell", "lipidchrysopourcent")
```


## DNA condensation in light depending on the division state
```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis'}
df <- res %>% filter(variable == "hetero.euch") %>% filter(value > -100) %>% filter(Lumiere == "Light")

pvalues <- c(0,0,0)
pindex <- c(0,0,0)


##

df_d <- filter(df, division == 0)$value
df_l <- filter(df, division == 1)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[1] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){
    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[1] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[1] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[1],5)))
}

##

df_d <- filter(df, division == 1)$value
df_l <- filter(df, division == 2)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

  if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[2] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[2] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[2] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[2],5)))
  }

##

df_d <- filter(df, division == 0)$value
df_l <- filter(df, division == 2)$value
n_d <- length(df_d) #number of points measured for the dark
n_l <- length(df_l)
large_sample <- as.integer( (n_d > 30) & (n_l > 30)) # =1 if sample large enough, 0 otherwise

  if( ((n_d < 3)|(n_l < 3)) | ((length(unique(df_d)) < 2)|(length(unique(df_l)) < 2) )) {
    print("Population size is too small to compare and/or all measures are the same")
    pvalues[3] <- 1
    }
  
if ( ((n_d >= 3)&(n_l >= 3)) & ((length(unique(df_d)) >= 2)&(length(unique(df_l)) >= 2) )){    #Are samples normally distributed? 
    normal_d <- shapiro.test(df_d)$p.value
    normal_l <- shapiro.test(df_l)$p.value
    N = as.integer(normal_d > 0.05) & (normal_l > 0.05)
    if (N == 1) { #samples normally distributed
      #Same variances?  
      NVar <- as.integer(var.test(df_d,df_l)$p.value > 0.05)
      if (NVar == 1) { #same variances
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = T, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with equal variances), alpha = 5%"
      }
      else { #different variances
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples normally distributed with different variances), alpha = 5%"
      }
    }
    else{ #variables not normally distributed 
      if (large_sample == 1) {
        #Sample large enough to do a student test to compare the means
        pvalues[3] <- t.test(x = df_d, y = df_l, alternative ="two.sided", var.equal = F, conf.level = 0.95)$p.value
        test_used <- "Two-sided Student test (samples not normally distributed but large enough - n > 30), alpha = 5%"
      }
      if (large_sample == 0) {
       pvalues[3] <- wilcox.test(x = df_d, y = df_l, alternative ="two.sided", conf.level = 0.95)$p.value
        test_used <- "Two-sided Wilcoxon test (small samples not normally distributed), alpha = 5%"
      }
    }
    print(paste0(test_used, ", p-value = ", round(pvalues[3],5)))
  }
```

```{r, echo=FALSE, warning = FALSE, message = FALSE, results = 'asis', fig.width = 5, fig.height = 5.8, fig.align = "center"}

for (i in c(1,2,3)) {
  psign <- c("NS","*", "**", "***")
  pindex[i] <- as.integer(pvalues[i] >= 0.05) + 
      as.integer((pvalues[i] < 0.05) & (pvalues[i] >= 0.01))*2 + 
      as.integer((pvalues[i] < 0.01) & (pvalues[i] >= 0.001))*3 +
      as.integer(pvalues[i] < 0.001)*4
}
  
df[33,3] = 1
  
plot2 <- ggplot(df, aes(x=factor(division) , y=value, fill = factor(division))) + 
    geom_violin() + 
    geom_jitter(size = 0.2, width = 0.1, height = 0.05) +
    stat_summary(fun = "mean", geom = "crossbar", color = "black", 
                size = 0.3) + 
    stat_summary(fun.data = "mean_cl_normal", geom = "errorbar", 
                 color = "black",
                 width = 0.4, alpha = 0.7) + 
    theme(axis.title.x=element_blank(),
          axis.title.y = element_text(size = 15),
          axis.text.y = element_text(size = 15), 
          legend.position = "none",
          plot.title = element_text(size = 15, margin = margin(c(0,0,0.5,0), unit = "in")))+
  scale_fill_manual(values = c("#F7C090", "#feefae", "#A9DFD0")) +
  scale_x_discrete(labels = c("Non-dividing cell", "Recently divided cell", "Dividing cell")) +
    geom_signif(annotations = c(psign[pindex]), y_position = c(270,270,310), xmin = c(1.02,2.02,1.02), xmax = c(1.98,2.98,2.98)) +
    ggtitle("DNA condensation, depending on the state of the cell")
 
  print(plot2)
  ggsave(plot2, file=paste0("DNA condensation",".png"), width = 5, height = 5.8, units = "in", dpi=300)

```